---
title: "daily_consumer"
author: "muhammad shamoon"
date: "2024-04-11"
output: html_document
---


## Installing and loading common packages and libraries

```{r}
install.packages('tidyverse')
library(tidyverse)
```
## Loading CSV files

Here we'll create a dataframe named 'daily_activity' by doing union between two CSV files from the dataset.

```{r}
daily_activity_apr <- read.csv("dailyActivity_merged_mar-apr.csv")
daily_activity_may <- read.csv("dailyActivity_merged_apr-may.csv")
```


```{r}
daily_activity <- rbind(daily_activity_apr,daily_activity_may)
```


## Exploring the table

```{r}
colnames(daily_activity)
```

```{r}
n_distinct(daily_activity$Id)
```

## Finding the percentage of everyday consumers

The normal values for daily steps, calories burned and sedentary minutes for females can vary but we can segment everday consumers by applying general boundary values.

```{r}
everyday_consumer <- daily_activity %>%
  filter(TotalSteps > 5000 &
         Calories > 1200 &
         SedentaryMinutes < 8*60) %>%
#  distinct(Id) %>%
  summarise(percentage = n_distinct(Id) / n_distinct(daily_activity$Id) * 100)
```

```{r}
everyday_consumer$percentage
```